Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Consistency in naive spelling and fixed-point hyphenation.

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
% \usepackage{xltxtra}
% \setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
%
\input{preamble}

@@

This article contributes a step by step process for going from a naive
analyzer derived under the abstracting abstract machine approach, to
an efficient program analyzer.  The end result of the process is a two
to three order-of-magnitude improvement over the systematically
derived analyzer, making it competitive with hand-optimized
implementations that compute fundamentally less precise results.
\end{abstract}

@@

We can cast this exploration process in terms of a fixed-point calculation.
%
Given the initial state $\varsigma_0$ and the transition relation $\machstep$,
we define the global transfer function:
\begin{equation*}
 F_{\varsigma_0} : \mathcal{P}(\mathit{State}) \to \mathcal{P}(\mathit{State})
 \text.
\end{equation*}
Internally, this global transfer function computes the successors of all supplied states, and then includes the inital state:
\begin{equation*}
  F_{\varsigma_0}(S) = \{ \varsigma_0 \} \cup \{ \varsigma' \mathrel{|} \varsigma \in S \text{ and } \varsigma \machstep \varsigma' \}\text. 
\end{equation*}
Then, the evaluator for the analysis computes the least fixed point of the global transfer function:
\begin{equation*}
 \eval(e) = \mathrm{lfp}(F_{\varsigma_0})\text{,}
\end{equation*}
where $\varsigma_0 = \ev[^\mtcntr]{e, \varnothing, \varnothing, \kmt}$.

To conduct this naive exploration on the \Church{} example would require
considerable time.  Even though the state space is finite, it is exponential in
the size of the program.  Even with $k = 0$, there are exponentially many
stores in the AAM framework.

@@

\subsubsection{Na\"ively}

@@

\subsubsection{Less na\"ively and less precisely}

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\naive}{na\"ive}
\newcommand{\naively}{na\"ively}
\newcommand{\Naive}{Na\"ive}
\newcommand{\Naively}{Na\"ively}
% \usepackage{xltxtra}
% \setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
%
\input{preamble}

@@

This article contributes a step by step process for going from a \naive
analyzer derived under the abstracting abstract machine approach, to
an efficient program analyzer.  The end result of the process is a two
to three order-of-magnitude improvement over the systematically
derived analyzer, making it competitive with hand-optimized
implementations that compute fundamentally less precise results.
\end{abstract}

@@

We can cast this exploration process in terms of a fixed-point calculation.
%
Given the initial state $\varsigma_0$ and the transition relation $\machstep$,
we define the global transfer function:
\begin{equation*}
 F_{\varsigma_0} : \mathcal{P}(\mathit{State}) \to \mathcal{P}(\mathit{State})
 \text.
\end{equation*}
Internally, this global transfer function computes the successors of all supplied states, and then includes the inital state:
\begin{equation*}
  F_{\varsigma_0}(S) = \{ \varsigma_0 \} \cup \{ \varsigma' \mathrel{|} \varsigma \in S \text{ and } \varsigma \machstep \varsigma' \}\text. 
\end{equation*}
Then, the evaluator for the analysis computes the least fixed-point of the global transfer function:
\begin{equation*}
 \eval(e) = \mathrm{lfp}(F_{\varsigma_0})\text{,}
\end{equation*}
where $\varsigma_0 = \ev[^\mtcntr]{e, \varnothing, \varnothing, \kmt}$.

To conduct this \naive exploration on the \Church{} example would require
considerable time.  Even though the state space is finite, it is exponential in
the size of the program.  Even with $k = 0$, there are exponentially many
stores in the AAM framework.

@@

\subsubsection{\Naively}

@@

\subsubsection{Less \naively and less precisely}
